Communication Efficient Learning towards Crowdsourcing Applications

### 2017-04-10 draft/draft.tex
draft abstract

\begin{abstract}
submit  abstract until 13.04

>>>>

\begin{abstract}
Learning from multiple sources of labeled data can increase the confidence of a machine learning system, if the expertise of different labelers can efficiently be assembled. However, using a large amount of labelers in the test time can be expensive on the long run. For instance, in crowdsourcing we have to pay each labeler in order to get the annotations. In a scenario of Internet of Things, obtaining data from multiple sensors means high communication overhead. Nevertheless, in many situations a small set of competent experts could already constitute a very accurate labeling system, while keeping a low cost of communication with the labelers. We design a methodology for training a classification system where data labels are obtained from a small set of labelers and the labelers are weighted optimally in order to offer high classification accuracy. We define an optimization procedure where sparsity of the client vector that weighs the labelers is controlled while reducing a classification error. Using this procedure, we obtain results close to the classification performance when using the original set of labelers, while reducing the number of those by over 60\%.

%submit  abstract until 13.04
